\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-30 manuscript.Rnw
Minor updaters with summary.ce() and icer() functions

For a given subgroup, QALYs and costs are simulated for each PSA sample, treatment strategy, and health state. They are summarized with the \code{$summarize()} method, which first sums across health states and then computes a (weighted) average across patients, by PSA sample, treatment strategy, and subgroup. The output is a generic cost-effectiveness object (of class \code{ce}) that can be used to perform CEA as demonstrated in Section~\ref{sec:cea}. Here, we use the \code{summary()} method to summarize the results.

<<ictstm_summarize>>=
ce_sim_ictstm <- ictstm$summarize()
summary(ce_sim_ictstm)
@

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
summary(ce_sim_psm)
@

@@

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
summary(ce_sim_cdtstm)
@

@@

A CEA is performed from this output with the \code{cea()} and \code{cea_pw()} functions. \code{cea()} summarizes results by simultaneously accounting for each treatment strategy in the analysis, while \code{cea_pw()} summarizes ``pairwise'' results in which each treatment is compared to a comparator.

@@

<<cea_icer>>=
library("magrittr")
icer(cea_pw_ictstm, k = 100000, 
     strategy_values = strategies$strategy_name[-1]) %>%
  format()
@

>>>>

For a given subgroup, QALYs and costs are simulated for each PSA sample, treatment strategy, and health state. They are summarized with the \code{$summarize()} method, which first sums across health states and then computes a (weighted) average across patients, by PSA sample, treatment strategy, and subgroup. The output is a generic cost-effectiveness object (of class \code{ce}) that can be used to perform CEA as demonstrated in Section~\ref{sec:cea}. Here, we use the \code{summary()} method to summarize the results and make use the ``pipes'' from the \pkg{magrittr} to nicely format the output.

<<ictstm_summarize>>=
library("magrittr")
ce_sim_ictstm <- ictstm$summarize()
summary(ce_sim_ictstm, 
        strategy_values = strategies$strategy_name) %>%
  format()
@

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
summary(ce_sim_psm, 
        strategy_values = strategies$strategy_name) %>%
  format()
@

@@

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
summary(ce_sim_cdtstm, 
        strategy_values = strategies$strategy_name) %>%
  format()
@

@@

A CEA is performed from this output with the \code{cea()} and \code{cea_pw()} functions. \code{cea()} summarizes results by simultaneously accounting for each treatment strategy in the analysis, while \code{cea_pw()} summarizes ``pairwise'' results in which each treatment is compared to a comparator (in this case SOC).

@@

<<cea_icer>>=
icer(cea_pw_ictstm, k = 100000, 
     strategy_values = strategies$strategy_name[-1]) %>%
  format()
@
